---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lookout

<!-- badges: start -->
[![R-CMD-check](https://github.com/sevvandi/lookout/workflows/R-CMD-check/badge.svg)](https://github.com/sevvandi/lookout/actions)
<!-- badges: end -->

**lookout** identifies outliers in data using leave-one-out kernel density estimates and extreme value theory. The bandwidth for kernel density estimates is computed  using persistent homology, a technique in topological data analysis. Using  peak-over-threshold method, a generalized Pareto distribution is fitted to the log of leave-one-out kde values to identify outliers. 

See [Kandanaarachchi and Hyndman (2021)](https://robjhyndman.com/publications/lookout/) for the underlying methodology.

## Installation

You can install the released version of lookout from [CRAN](https://CRAN.R-project.org) with:

``` r
#install.packages("lookout")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sevvandi/lookout")
```

## Example

```{r}
library(lookout)
lo <- lookout(faithful)
lo
autoplot(lo)
persistence <- persisting_outliers(faithful)
autoplot(persistence)
```
